---
title: "insights2.Rmd"
author: "Jay Gohner"
date: "November 14, 2019"
output: html_document
---

```{r}
suppressMessages(library("tidyverse"))
suppressMessages(library("knitr"))
suppressMessages(library("caret"))
purl("insights.rmd", output = "part1.r")
source("part1.r")
```
 
 Now we want to add a new column to our persons table. This column will hold the average rating that a person gave to a song.
 We will use functions from dplyr and the piping operator to create a vector of all the averages of song ratings by pseudonym.
 Then we will use the piping operator and another dplyr function to add this add our new column to the Person table.
 
```{r}
avg_song_rating <- Ratings %>% group_by(pseudonym) %>% summarise(avg_song_ratings = mean(rating))
Person <- inner_join(x = Person, y = avg_song_rating, by = "pseudonym")
```

We can now pick a variable to predict and build our model. We will subset Person, to get rid of columns like Timestamp and 
pseudonym generator, that have no effect on the model.

```{r}
set.seed(123)

select_Person <- select(Person, sex, academic_major, academic_level, year_born, avg_song_ratings)

sample_selection <- createDataPartition(select_Person$avg_song_ratings, p= .75, list=FALSE)

train <- select_Person[sample_selection, ]
test <- select_Person[-sample_selection, ]

train_model <- lm(avg_song_ratings ~., data = train)
summary(train_model)

predictions <- train_model %>% predict(test)
```
The p-value is terrible and overall the model isn't very good for predicting song ratings. Perhaps more having taken more data 
about more factors would've given us a more predictable model.